Rates of true polar wander in convecting planets

### 2014-07-02 tpw_rate.tex
Adjust formulae
Use equiv
A bunch of nonsense

%\documentclass[extra,onecolumn]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}

@@

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$ and the differences between the eigenvalues of the convective moment $\bf E$.
It is useful to define a nondimensional eigenvalue difference (or ``eigengap'') $\Lambda_{ij} = (\lambda_i - \lambda_j)/I_0$.  
With this we may rewrite this in terms of the nondimensional numbers defined above, where 
$\varepsilon \sim \mathrm{Fr}$ and $\tau \sim \eta / \rho g R = \frac{R^2}{\kappa} \Gamma/\mathrm{Ra}$.

@@

\section{Scaling}

@@

@@

\section{Degree-two moments}

@@

We may therefore go into the principle coordinate system of both tensors to find
\begin{equation}
{\bf I} = \begin{bmatrix}
\int_V \rho (y^2+z^z)\\
\int_V \rho (x^2+z^2) \\
\int_V \rho (x^2+y^2) 
\end{bmatrix}^T {\bf 1}
\end{equation}

\begin{equation}
{\bf Q} = \begin{bmatrix}
\int_V \rho (2 x^2 - y^2 - z^z)\\
\int_V \rho (2 y^2 - x^2 -z^2)\\
\int_V \rho (2 z^2 - x^2 - y^2) 
\end{bmatrix}^T {\bf 1}
\end{equation}

@@

\begin{equation}
{\bf Q} = \begin{bmatrix}
(\lambda_2-\lambda_1) + (\lambda_3-\lambda_1)\\
(\lambda_1-\lambda_2) + (\lambda_3-\lambda_2)\\
(\lambda_1-\lambda_3) + (\lambda_2-\lambda_3)\\
\end{bmatrix}^T {\bf 1}
\label{maccullagh}
\end{equation}

>>>>

%\documentclass[extra,onecolumn]{gji}
\documentclass[extra]{gji}
\usepackage{timet}
\usepackage{amsmath}
\usepackage{graphicx}

@@

These equations are a version of what has been called the ``Milankovitch theorem'' \citep{munk1960rotation}.  
Written this way, it is clear that the important quantities are $\theta$ and the differences between the eigenvalues of the convective moment $\bf E$.
It is useful to define a nondimensional eigenvalue difference (or ``eigengap'') $\Lambda_{ij} \equiv (\lambda_i - \lambda_j)/I_0$.  
With this we may rewrite this in terms of the nondimensional numbers defined above, where 
$\varepsilon \sim \mathrm{Fr}$ and $\tau \sim \eta / \rho g R = \frac{R^2}{\kappa} \Gamma/\mathrm{Ra}$.

@@

\section{Scaling}
\subsection{An estimate of $\Lambda_{ij}$}

\begin{figure}
\label{misfit}
\includegraphics[]{figures/eigengap.pdf}
\caption{Oooga}
\end{figure}

\begin{figure}
\label{misfit}
\includegraphics[width=10cm]{figures/perturb.pdf}
\caption{Oooga}
\end{figure}

@@

For thermal convection, the convective part of the moment of inertia $\bf E$ is directly related to the degree-two structure of the temperature field (see Appendix \ref{appendix:moments}).
Therefore, an estimate of one allows an estimate of the other.

The structure of thermal convection is primarily controlled by the Rayleigh number.  Once the Rayleigh number is sufficiently high ($\sim10^6$) 
the style of convection changes from steady/quasisteady to chaotic.  Accompanying this transition to chaos is the broadening of the spatial 
and temporal spectra \citep{mclaughlin1982transition}.

We can expand the temperature structure of the convecting planet with a set of orthogonal basis functions $X_{lmn}$, 
where $l$, $m$, and $n$ are wavenumbers in the $x$, $y$, and $z$ directions, respectively.  
\begin{equation} 
T( x, y ,z )  = {\displaystyle \sum_{l m n} } T_{lmn} X_{lmn} (x , y, z)
\end{equation}

For chaotic thermal convection  there will be some power in every mode $X_{lmn}$ up to some wavenumber.  
At that critical wavenumber thermal diffusivity will

\subsection{An estimate of the mismatch $\theta$}

\citet{davis1970rotation}

\begin{figure}
\label{misfit}
\includegraphics[width=10cm]{figures/misfit.pdf}
\caption{Oooga}
\end{figure}

@@

\section{Degree-two moments}
\label{appendix:moments}

@@

We may therefore go into the principle coordinate system of both tensors to find
\begin{equation}
{\bf I} = {\bf 1} \begin{bmatrix}
\int_V \rho (y^2+z^z)\\
\int_V \rho (x^2+z^2) \\
\int_V \rho (x^2+y^2) 
\end{bmatrix}
\end{equation}

\begin{equation}
{\bf Q} = {\bf 1} \begin{bmatrix}
\int_V \rho (2 x^2 - y^2 - z^z)\\
\int_V \rho (2 y^2 - x^2 -z^2)\\
\int_V \rho (2 z^2 - x^2 - y^2) 
\end{bmatrix}
\end{equation}

@@

\begin{equation}
{\bf Q} = {\bf 1} \begin{bmatrix}
(\lambda_2-\lambda_1) + (\lambda_3-\lambda_1)\\
(\lambda_1-\lambda_2) + (\lambda_3-\lambda_2)\\
(\lambda_1-\lambda_3) + (\lambda_2-\lambda_3)\\
\end{bmatrix}
\label{maccullagh}
\end{equation}
